`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
correction to the appendix
added field decomposition plot

\begin{figure}\label{fig:2d_kernel}

@@

@@

where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$. %The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}. 

@@

		\mathbf e_t=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 

@@

\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 

@@

	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\

@@

The covariance of $\mathbf{e}_t$ is 

@@

	\lefteqn{\mathbf{\Sigma}_e} \nonumber \\ 

>>>>

@@

 	\label{fig:2d_kernel}

@@

where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$. An example of the field decomposition is given in Figure~\ref{fig:FieldDecomposition}.%The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}.
   		\includegraphics{./Graph/FieldDecomposition.pdf} 
   	\caption{An example of continuous field decompposed by a finite number of basis functions scaled by the state vector. } 
	\label{fig:FieldDecomposition}

@@

		\mathbf e_t(\mathbf r)=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 

@@

\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t(\mathbf r)$ is given by 

@@

	\mathbf E\left[ \mathbf e_t(\mathbf r)\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\

@@

The covariance of $\mathbf{e}_t(\mathbf r)$ is 

@@

	\lefteqn{\mathbf E\left[ \mathbf e_t(\mathbf r) \mathbf e_t^\top(\mathbf r')\right]} \nonumber \\ 
